ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-07-05 paper.tex
Added new suggested figures

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/system_use.png} \hfil
  \includegraphics[width=0.45\textwidth]{figures/system_use.png}
  \caption{The system in use during an experiment with a blindfolded participant. \tofix{can you add another image with (most of) the objects? maybe arranged in a grid} }\label{fig:system-in-use}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.45\columnwidth]{figures/desk_example.png} \hfil
  \includegraphics[width=0.45\columnwidth]{figures/desk_example.png}
  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects. \tofix{add one more image, different from VISAPP though}}\label{fig:openimage}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment.\tofix{Half the height of the image. You can also put it together with Fig.~4 to save space.}}\label{fig:boxplot-displacement}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/system_use.png} \hfil
  \includegraphics[width=0.45\textwidth]{figures/object_grid/grid.png}
  \caption{The system in use during an experiment with a blindfolded participant. \tofix{can you add another image with (most of) the objects? maybe arranged in a grid} }\label{fig:system-in-use}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.35\columnwidth]{figures/desk_example.png} \hfil
  \includegraphics[width=0.55\columnwidth]{figures/kitchen_example_thicc.png}
  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects.}\label{fig:openimage}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=1.0\textwidth]{figures/boxplot_combined.png}
  \caption{A set of boxplots comparing the total linear and angular displacements, as well as the time to target for each experiment. }\label{fig:boxplot-time}
\end{figure}

@@

%\begin{figure}[t]
  %\centering
  %\includegraphics[width=0.6\textwidth]{figures/boxplot_displacement.png}
  %\caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment.\tofix{Half the height of the image. You can also put it together with Fig.~4 to save space.}}\label{fig:boxplot-displacement}
%\end{figure}
